Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
rev

@@

\begin{frame}{ML: Translucent Sums}
\begin{itemize}
\item values representing modules
\item translucent sum: sequence of bindings; translucent sum type:
  sequence of declarations
\item differs from traditional records, because later fields can
  depend on earlier ones
\item allows any type to be partially or fully deermined by a type
\end{itemize}
\end{frame}

@@

\begin{frame}{ML: Path-Dependent Types}
\begin{itemize}
\item Scala's abstract types have close resemblances to abstract types
  of signatures in these ML-like module systems. In particular, in
  their calculus, there's a form of dependent type, since translucent
  sums are terms that may contain types.
\item More concretely, their so-called VALUE rules enable a
  translucent sum to be given a more precise type by referring to the
  names of its type members with a path selection -- this ability
  based on path-dependent types is not only essential for breaking the
  dependencies between (sub)fields but also critical for the
  propagation of typing information.
\item Compared to Scala, these path-dependent types are more limited
  because recursive references and bounded quantifications are not
  allowed.
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Hello}
\begin{minted}{scala}
object HelloWorld extends App {
  println("Hello, World")
}
\end{minted}
\end{frame}

>>>>

\begin{frame}[fragile]{SML modules: Example}
TODO
\end{frame}

@@

\begin{frame}{ML: Translucent Sums}
\begin{itemize}
\item translucent sums are values representing modules
\item translucent sum: sequence of bindings
\item translucent sum type: sequence of declarations
\item unlike traditional records, later fields can depend on earlier ones
\item any type can be partially or fully determined by a type
\item dependent typing since translucent sums are terms that may contain type components
\end{itemize}
\end{frame}

@@

\begin{frame}{ML: Path-Dependent Types}
\begin{itemize}
\item Scala's abstract types  $\approx$ ML's abstract types of signatures; limitations:
\begin{itemize}
\item recursive references
\item bounded quantifications
\end{itemize}
\item translucent sum can be given a more precise type by referring to the name of its member path with a path selection; essential for
\begin{itemize}
\item breaking the dependencies between (sub)fields
\item propagation of typing information
\end{itemize}
\end{itemize}
\end{frame}

@@
